О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-23 pps-linear-bound/pps-linear-lower-bound.tex
Note about points in Construction are distinct

>>>>

	Note that all the points $M_{J\pm}$ are distinct:
	the equality $b_J = b_K$ implies $J=K$;
	the equality $b_J = b_K$ implies $c_J = -c_K$ or $c_J = a / c_k$.
	The first case is impossible because both $c_J$ and $c_K$ are positive;
	the second case contradicts with~\eqref{eq:a_equiv_3_mod_4} and~\eqref{eq:c_J_equiv_1_mod_4}.
